---
title: "Untitled"
author: "mary liu"
date: "10/20/2020"
output: html_document
---

```{r setup, include=FALSE}

library(base)
# install and load packages
library(knitr)
library(tidyverse)
library(magrittr)
library(naniar)
#install.packages('RcppBDT')
library(RcppBDT)
library(kableExtra)

opts_chunk$set(echo = FALSE, 
               warning = FALSE,
               message = FALSE)

pacman::p_load(
  "ggplot2",
  "knitr",
  "arm",
  "data.table",
  "foreign",
  "car",
  "faraway",
  "nnet",
  "reshape2",
  "VGAM"
)
#install.packages('readxl')
library(readxl)
```


```{r}
#load data
sp500 <- read_csv("C:/Users/49431/Downloads/GSPC.csv")


head(sp500)


data1 = sp500[c("Date","Adj Close","Volume")]
head(data1,15)


mean(sp500$turn_pre)
mean(sp500$turn_post)
```


```{r}
#sum(sp500$Volume)


data1[data1 == NA] = NA
# observations contains NA

num3 = complete.cases(sp500)
missing = data.frame(sp500)
#rownames(missing) = 'missing values'
gg_miss_var(missing) + theme(text = element_text(size=7)) +
  ylab('Number of Missing Values in Each Variable')
```


```{r}



for (i in 1998:2020){
  Mar <- getNthDayOfWeek(third, Fri, 3, i)
  Jun <- getNthDayOfWeek(third, Fri, 6, i)
  Sep <- getNthDayOfWeek(third, Fri, 9, i)
  Dec <- getNthDayOfWeek(third, Fri, 12, i)
  
  
  if ( i == 1998){
    quad_witching_date <- cbind.data.frame(Mar,Jun,Sep,Dec)
  }
  else{
    quad_witching_date <- rbind.data.frame(quad_witching_date, cbind.data.frame(Mar,Jun,Sep,Dec))
  }
}
quad_witching_date

quad_witching <- data.frame(day = c(quad_witching_date[,'Mar'], quad_witching_date[,'Jun'], quad_witching_date[,'Sep'], quad_witching_date[,'Dec']))
quad_witching
```

```{r}

#data1[data1$Date %in% quad_witching,]
#data1$Date %in% quad_witching
#is.element(data1$Date,c(quad_witching))
#data1[data1$Date == "1998-03-20",]

#typeof(data.frame(data1$Date))
data2 = data.frame(sp500[c("Date","Adj Close","Volume","Turnover","turn_pre","turn_post")])
head(data2)
#head(quad_witching)

data3 = data2[is.element(data2$Date,quad_witching$day),]
data3
```
```{r}
mean(data3$turn_pre)
mean(data3$turn_post)
plot(y= sp500$Turnover, x = sp500$Date, type = "l", main = "Overall Trend", xlab = "Date", ylab = "Turnover",col = "red")
```
```{r}
plot(y= data3$turn_pre, x = data3$Date, type = "b", main = "Turnover percentage (pervious day compare with current day)", xlab = "Date", ylab = "Turnover percentage")
plot(y= data3$turn_post, x = data3$Date, type = "b", main = "Turnover percentage (Postday compare with current day)", xlab = "Date", ylab = "Turnover percentage")
```

we made a new dataset adding 3 more variables: turnover, turn_pre and turn_post. Turnover is just multiplying adjust close and volume

turnover per: How much is today compared to yesterday, like the percentage increase/ decrease
turnover post percentage: How much is today compared to tmrw


the turnover varibale is easy to understand, but i wanna go a little more detail about the variable Turn_pre, we can see in this plot that most of the quaddurple day turnover pre percentage is above 0 percet. and there are only few which are below 0. we also calculated the average of turnover pre percent, which is 28.7% and cpmpare this with the average of overall turn_pre is a huge increase.

this is the plot for turnover post percenage. if we draw a line on y = 0, we can see there are only 4 dots thats either lay on the line or a little below it. but there are bunch of the points that's above and there are even 4 points thats like way way above it. 

so this also show that quadruple day also has a impact on turnover